---
title: "College Major Income"
author: "YukiKongJu"
date: "25/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(stringr)
library(dplyr)
library(tidyr)
library(forcats)
library(viridis)
library(hrbrthemes)
```

## Load Data

```{r }

folder <- "C:/Users/emuli/OneDrive/Documents/R/Projects/tidytuesday/college_majors/data/recent-grads.csv"
college_raw <- read.csv(file = folder, sep = ",", header = TRUE)

```

## Data Preprocessing

```{r  echo=FALSE}

college_processed <- college_raw %>%
  mutate(Major=str_to_title(Major)) 

college_processed$Major <- as.factor(college_processed$Major)

str(college_processed)

```

## Data exploration

### How much do new grad makes

```{r echo=FALSE}

# hist
college_processed %>% 
  ggplot(aes(Median))+
  geom_histogram()

# boxplot
college_processed %>% 
  mutate(Major_category = fct_reorder(Major_category, Median)) %>% 
  mutate(type=ifelse(Major_category=='Engineering', 'Highlighted', 'Normal')) %>% 
  ggplot(aes(Major_category, Median, fill=type, alpha=type))+
  geom_boxplot()+
  coord_flip()+
  scale_fill_manual(values = c("#69b3a2", "grey"))+
  scale_alpha_manual(values = c(1,0.1))+
  theme_ipsum()+
  theme(legend.position = "none")+
  xlab("Major Category")+
  ylab("Median Income ($)")


```

Note: There seems to be a spectrum ranging from STEM fields to liberal arts.

## Which major makes the most money

```{r}

college_processed %>% 
  arrange(desc(Median)) %>% 
  head(20) %>% 
  mutate(Major=fct_reorder(Major, Median)) %>%
  ggplot(aes(Major, Median))+
  geom_point( aes(color=Major_category),alpha=0.7)+
  geom_text(aes(label=Median), hjust=-1)+
  coord_flip()+
  ggtitle("Top 20 majors that make the most money")+
  xlab("Major")+
  ylab("Median ($)")

```

Note: We see that engineering majors make the most money.

```{r}

# preprocess data
majors_diff <- college_processed
majors_diff$Median_diff <- round(college_processed$Median- mean(college_processed$Median))
majors_diff$Median_type <- ifelse(majors_diff$Median_diff>0, "above", "below") %>% 
  as.factor()

# draw diverging barchart
majors_diff %>% 
  ggplot(aes(Major_category, Median_diff, label=Median_diff))+
  geom_bar(stat='identity', aes(fill=Median_type))+
  scale_fill_manual(name="Median Type", 
                    labels=c("Above Average", "Below Average"),
                    values = c("above"="#00ba38", "below"="#f8766d"))+
  coord_flip()+
  ggtitle("Will your earn more than the average graduate?")+
  xlab("Field")+
  ylab("Median Income ($)")

dir <- "C:/Users/emuli/OneDrive/Documents/R/Projects/tidytuesday/college_majors/images/average_income_diff.png"
ggsave(dir)

```



## Which majors is the most popular? among women?

```{r}

college_processed %>% 
  arrange(desc(Total)) %>% 
  head(20) %>% 
  mutate(Major=fct_reorder(Major, (Total))) %>% 
  gather(Gender, Number, Men, Women) %>% 
  ggplot(aes(Major,Total, fill=Gender))+
  geom_col()+
  coord_flip()

```
Note: Majors outside STEM field seem to be more popular among students, maybe because they are easier to get into.

```{r}

college_processed %>% 
  arrange(desc(Total))
  ggplot()

```


## What is the relationship between your sex and your income

```{r}

```


## Employment Rate

```{r}

college_processed %>% 
  arrange(desc(Employed)) %>% 
  head(20) %>% 
  mutate(Employed=fct_reorder(Major_category, desc(Employed))) %>% 
  gather(Employement, Number, Full_time, Part_time, Unemployed) %>% 
  ggplot(aes(Major_category, Employed, fill=Employement))+
  geom_col()+
  coord_flip()

```


```{r}





```

## What to explore next

  * Is your major worth taking? (income vs cost, job that requires no degree)
  * Will you find a job after graduating (employed, full-time, part-time, unemployed, unemployment rate)
