---
title: "Untitled"
author: "Emulie Chhor"
date: "01/01/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(stats)
```


### Loading the data

```{r}
college <- read.csv("~/Projects/tidytuesday/college_majors/data/recent-grads.csv")
```

### Exploring the data

```{r}
names(college)
summary(college)
college %>% 
  group_by("Major_category") %>% 
  summarise(mean(Employed), mean(Median))
```

## Making the stem dataset

```{r}
unique(college$Major_category)
stem_categories <- c("Engineering", "Business", 
  "Computers & Mathematics", "Biology & Life Science", "Physical Sciences")
non_stems_categories <- c("Law & Public Policy", "Agriculture & Natural Science", "Industrial Arts & Consumer Services", "Arts", "Health", "Social Science", "Education", 
  "Humanities & Liberal Arts", "Psychology & Social Work", 
  "Communications & Journalism", "Interdisciplinary")
df_stem <- college %>% 
  mutate(is_stem = ifelse(Major_category %in% stem_categories, "stem", "non-stem"))
```

### a) are there really more men in STEM than in non-STEM majors?

H0: There is no difference between the proportion of women in STEM and non-STEM 
  fields $p1-p2 = 0$
H1: There is a difference between the proportion of women in STEM and non-STEM $p1-p2 != 0$

We will choose $\alpha=0.5$, a confidence interval of 95% percent.

We have a bilateral test: $P(|t|>t_{n-2}(0.025))$

```{r}
# this code generate NA not because there are NA values, but because there is a 0 value making a division by 0
tmp <- df_stem %>% 
  filter(!is.na(ShareWomen)) %>% 
  dplyr::group_by(is_stem) %>% 
  summarise_at(c("ShareWomen"), funs(mean = mean, sd = sd, count = dplyr::n()))

# we are applying Laplace correction to avoid the division by 0
gender_stem <- df_stem %>% 
  filter(!is.na(ShareWomen)) %>% 
  mutate(women_prop = (Women + 1) / Total) %>% 
  dplyr::group_by(is_stem) %>% 
  summarise_at(c("women_prop"), funs(mean = mean, sd = sd, count = dplyr::n()))

# calculating the p-value
n <- with(gender_stem, count[1]+ count[2])
t <- with(gender_stem, abs((mean[1] - mean[2]) / (count[1]/ n * sd[1] + count[2] / n * sd[2])))
2 * pt(t, df = n - 2, lower.tail = FALSE)
```

Since the p-value = 0.222 > 0.05, we can't reject H0. There is not enough evidence 
to say that the proportion of STEM and non-STEM major gender proportion is different.

## b) Do STEM major make more money than non-STEM majors?

H0: There is no difference between the mean median of stem vs non-stem majors (p1 - p2 == 0)
H1: There is a difference between the mean median of stem vs non-stem majors (p1 - p2 > 0)

Unilateral test

```{r}

num_students <- sum(college[1:3, "Total"])
num_students <- sum(college$Total, na.rm = TRUE)
tmp <- df_stem %>% 
  filter_at(vars(Total, Median), all_vars(!is.na(.))) %>% 
  mutate(weights = Total / sum(Total)) %>% 
  group_by(is_stem) %>% 
  summarise(mean = (sum(weights * Median) / sum(weights)),
            sd = sum(weights * (Median - mean))^2, 
            count = sum(Total))



# calculate pvalue
n <- with(tmp, count[1]+ count[2])
t <- with(tmp, abs((mean[2] - mean[1]) / (count[1]/ n * sd[1] + count[2] / n * sd[2])))
# pt(t, df = n - 2, lower.tail = FALSE)
pchisq(t, df = n - 2, lower.tail = FALSE)

# alternative method
chisq.test(tmp$mean)

```
The pvalue is around 0, which mean that we reject H0. Therefore, there is 
enough evidence to say that STEM the median salary of stem majors graduates 
is bigger than non-stem majors.

## c) Are stem majors more employable? What is their emloyment rate?

H0: the unemployment rate for stem and non-stem majors are the same (p1-p2 = 0)
H1: the unemployment rate for non-stem is bigger than stem major (p1-p2 > 0)

unilateral test

```{r}
tmp <- df_stem %>% 
  group_by(is_stem) %>% 
  summarise(mean = mean(Unemployment_rate), 
            sd = mean(Unemployment_rate))

chisq.test(tmp$mean)
```

Since pvalue<0.05, we reject H0 and we say that unemployment rate for non-stem 
major is bigger than for stem majors.

## d) Do non-stem majors use their diplomas less than stem majors?

H0: There is no difference in the  percentage of stem and non-stem majors that use their diplomas 
H1: Non-stem majors use their diplomas less than stem majors


```{r}
# using laplace correction
tmp <- df_stem %>% 
  filter_at(vars(College_jobs, Non_college_jobs), all_vars(!is.na(.))) %>% 
  mutate(diploma_usage= (1 + College_jobs) / (College_jobs + Non_college_jobs + 1)) %>% 
  group_by(is_stem) %>% 
  summarise(mean = mean(diploma_usage), 
            sd = sd(diploma_usage), 
            count = n())

n <- with(tmp, count[1]+ count[2])
t <- with(tmp, abs((mean[2] - mean[1]) / (count[1]/ n * sd[1] + count[2] / n * sd[2])))
pt(t, df = n - 2, lower.tail = FALSE)
```

Since pvalue>0.05, we say that there is not enough evidence to reject H0. Therefore, 
we say that stems and non-stems major use their diplomas just as much.

