---
title: "Untitled"
author: "Emulie Chhor"
date: "01/01/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(GGally)
library(knitr)
library(stats)
```

### Loading the data

```{r}
college <- read.csv("~/Projects/tidytuesday/college_majors/data/recent-grads.csv")
```

### Which variables are the most important when predicting salary

Model 1: using all variables
```{r}
names(college)

# checking pairs and correlation
college_numeric <- college[, sapply(college, is.numeric)]
# ggpairs(college_numeric)

# plot 
with(college, plot(ShareWomen, Median))

# creating the model
df <- college %>% 
  select(-c("Rank", "Major_code"))

model1 <- lm(Median~Total+Men+Women+factor(Major_category)+ ShareWomen + Employed 
      + Full_time + Part_time + College_jobs + Non_college_jobs + Low_wage_jobs, data = college)

# summary(model1)$coefficients

# standardized residual plots
plot(fitted(model1), residuals(model1), col='seagreen')
abline(h=mean(residuals(model1)))


```

By plotting the scatterplot, it seems that the data is linear. Also, the 
assumptions for the linear regression are met: 
- independance of errors: there is no relationship between residuals
- mean residuals is 0
- homoscedaticity: the residuals variance is constant across all values.

However, when plotting the standardized residuals plot, it seems that there is 
a few outliers. We will plot the jacknived residuals and cook's Distance to 
find and remove any outliers from our model

```{r}

which.max(residuals(model1))

# finding outliers with 1.5 IQR
residuals_model1 <- residuals(model1)
Q1 <- quantile(residuals_model1, 0.25)
Q3 <- quantile(residuals_model1, 0.75)
IQR <- Q3 - Q1
lower <- Q1 - 1.5 * IQR
upper <- Q3 + 1.5 * IQR
outliers_iqr <- which(residuals_model1 < lower | residuals_model1 > upper)
college[outliers_iqr, ]

# with Cook's Distance
plot(fitted(model1), cooks.distance(model1), main = "Cook Distance", col='seagreen', 
     xlab = "", ylab = "")
cook_threshold <- 1 / (nrow(college) -2 -1)
outliers_cook <- which(residuals_model1 > cook_threshold)

college_no_outliers <- college[-outliers_iqr, ]
```

We are going to fit the data with no outliers onto a multiple linear regression

```{r}
names(college_numeric)
college_numeric_no_outliers <- college_no_outliers[, sapply(college, is.numeric)] %>% 
  select(-c("Rank", "Major_code"))

model2 <- lm(Median~. , data = college_numeric_no_outliers)
residuals_model2 <- residuals(model2)
kable(summary(model2)$coefficients)
```
By taking $\alpha=0.05$, the variable that are significative in our model 
are: 
- ShareWomen
- Unemployment_rate
- P25th, P75th

Let's build a third model with these variables only and perform a F test 
to find the best model between these 3

```{r}
model3 <- lm(Median ~ ShareWomen + Unemployment_rate + P25th + P75th, 
             data = college_numeric_no_outliers)

summary(model3)$fstatistic[1]
summary(model2)$fstatistic[1]
summary(model1)$fstatistic[1]
```
Since the model 3 has the largest F statistic, we say it is the best fit.

## b) TODO: What majors are dominated by men? by women?

```{r}
tmp <- college %>% 
  group_by(Major_category) %>% 
  mutate(weights = Total / sum(Total))

```


