---
title: "Exploring the survivors dataset"
output: html_document
---

```{r , include=FALSE}

# system('sudo apt install libcairo2-dev')
# devtools::install_github("hrbrmstr/hrbrthemes")
# https://dabblingwithdata.wordpress.com/2018/01/02/my-favourite-r-package-for-summarising-data/

library(tmap)
library(maps)
library(usmap)
library(spData)
# library(spDataLarge)
library(sf)
library(raster)
library(leaflet)
library(survivoR)
library(ggplot2)
library(lubridate)
library(hrbrthemes)
library(plotly)
library(tidyr)
library(dplyr)

castaway_details <- survivoR::castaway_details
castaways <- survivoR::castaways
challenge_description <- survivoR::challenge_description
challenge_results <- survivoR::challenge_results
challenges <- survivoR::challenges
confessionals <- survivoR::confessionals
hidden_idols <- survivoR::hidden_idols
jury_votes <- survivoR::jury_votes
season_palettes <- survivoR::season_palettes
season_summary <- survivoR::season_summary
tribe_colours <- survivoR::tribe_colours
tribe_mapping <- survivoR::tribe_mapping
viewers <- survivoR::viewers
vote_history <- survivoR::vote_history
```


# Data Wrangling


```{r}


```


Inspiration: https://gradientdescending.com/survivor-data-from-the-tv-series-in-r/

# Survivors Location



# Castaways - Exploring Players Stats

Where do players come from?

```{r }
# tm_shape(usmapdata::us_map) +
#   tm_fill() +
#   tm_borders()




```

Players occupations/jobs

```{r}
castaway_details%>% 
  distinct(castaway_id, occupation) %>% 
  group_by(occupation) %>% 
  transmute(n = n()) %>% 
  arrange(desc(n)) %>% 
  unique()

# get players by occupation

get_players_by_occupation <- function(query){
  players <- castaway_details %>% 
    filter(grepl(query, occupation)) %>% 
    select(c(castaway_id, full_name, occupation))
  return(players)
}

get_players_by_occupation('Student')
get_players_by_occupation('Bartender')
get_players_by_occupation('Trainer')
get_players_by_occupation('Sales')
get_players_by_occupation('Officer')
get_players_by_occupation('Model')
get_players_by_occupation('Teacher')
get_players_by_occupation('Manager')
get_players_by_occupation('Waiter|Waitress')
get_players_by_occupation('Engineer')


```

Who played the most

```{r}
participations_count <- castaways %>% 
  group_by(castaway_id) %>%
  mutate(num_participations=n()) %>% 
  select(c(castaway_id, full_name, num_participations)) %>% 
  unique() %>% 
  arrange(desc(num_participations), castaway_id)
```

### Memorable players - Played at least two seasons or made the jury

```{r, echo=FALSE}

num_players <- as.integer(nrow(castaways %>% select(castaway_id) %>% distinct() %>% arrange(castaway_id)))

went_far <- castaways %>% 
  filter(!is.na(jury_status) | (result %in% c('Sole Survivor', 'Runner-up'))) %>% 
  group_by(castaway_id, full_name) %>% 
  summarise(has_made_jury=TRUE) 

has_made_jury <- castaways %>% 
  select(castaway_id, full_name) %>% 
  distinct() %>% 
  left_join(went_far) %>% 
  mutate(has_made_jury=ifelse(is.na(has_made_jury), FALSE, TRUE)) %>% 
  arrange(castaway_id)

players <- castaways %>% 
  select(castaway_id, full_name) %>% 
  left_join(participations_count, by=c("castaway_id", "full_name")) %>% 
  left_join(has_made_jury, by=c("castaway_id", "full_name"))

```

```{r, echo=FALSE}

mediocre_players <- players %>% 
  filter(has_made_jury==FALSE & (num_participations == 1))

okay_players <- players %>% 
  filter((has_made_jury==FALSE) & (num_participations > 1)) 

memorable_players <- players %>% 
  filter((has_made_jury==TRUE) & (num_participations > 1))

winners <- castaways %>% 
  filter(result == 'Sole Survivor')

get_winners <- function() {
   tmp <- castaways %>% 
    filter(result == c("Sole Survivor", "Runner-up"))
   return(tmp)
}

winners_runnerups <- get_winners()

# winners who played one time


# goats <- players %>% 
#   filter((has_made_jury==TRUE) & (num_participations > 2)) 


```



# Challenges 

Types of challenges

```{r }
within(challenge_description, rm(challenge_id, challenge_name)) %>% 
  summarise_each( funs = mean) %>% 
  sapply(round, 3) * 100
```




# Winners - 

### Winners confessionals vs rest of people

```{r , echo=FALSE}
# num_confessionals <- aggregate(confessionals$confessional_count, by=list(Season=confessionals$season_name, Cast=confessionals$castaway, ID = confessionals$castaway_id), FUN=sum)

num_confessionals <- confessionals %>% 
  semi_join(castaways, by ="castaway_id") %>% 
  group_by(season_name, season, castaway, castaway_id) %>% 
  summarise(Confessional_Count=sum(confessional_count)) %>% 
  arrange(season, desc(Confessional_Count))

confessions <- num_confessionals %>% 
  inner_join(castaways, by=c("castaway_id", "season_name", "season")) %>% 
  select(c("season", "season_name",  "full_name", "castaway_id", "Confessional_Count", "result", "personality_type", "total_votes_received", "immunity_idols_won")) %>% 
  arrange(season, desc(Confessional_Count)) 

# TODO: add ranking


num_confessionals %>% 
  ggplot(aes(x=, y=Confessional_Count))
```


### Winners Personality Types (vs norm)

Il y a 16 types de personnalités. On s'attend à ce que le nombre de personnes dans chaque classe représente autour de 1/16 ie 6.25%

```{r , echo=FALSE}


personality_count <- castaways %>% group_by(personality_type) %>% summarise(count= n()) 
personality_count$perc <- personality_count$count / nrow(castaways) * 100 

# sort winners by introvert and extrovert
introvert_count <- function(df) {
  df$is_introvert <- ifelse(substr(df$personality_type,1,1) == "I", TRUE, FALSE)
  introvert_count <- df %>% group_by(is_introvert) %>% summarise(count = n())
  return(introvert_count)
}

introvert_count(winners)
introvert_count(castaways)

# personality count
castaways %>% 
  group_by(personality_type) %>% 
  summarise(Freq = n()) %>% 
  arrange(desc(Freq))

```

### Sort by personality_type

```{r, echo=False}

personality_types <- c("ENTP", "INTP", "ESTP", "ISTP", "ESFP", "ISFP", 
  "ESFJ", "ISFJ", "ESFP", "ISFP", "ENTJ", "INTJ", "ENFJ", "INFJ", "ENFP", "INFP")

get_players_by_MBIT <- function(type) {
  tmp <- castaways %>% 
    filter(personality_type == type)
  return(tmp)
}

get_players_by_MBIT("ISTP")

```

### Which personality type is more likely to make alliances/work together

```{r, echo=False}


```

### Winners votes out 

```{r , echo=FALSE}

plot_lm <- function(x, y) {
  reg <- lm(y~x)
  summary(reg)
  plot(x, y)
  abline(reg, col='red')
}

plot_lm(castaways$day, castaways$total_votes_received)

```

Le nombre de votes n'est pas un bon prédicteur pour déterminer le gagnant

### Immunity Idols

```{r}
plot_lm(castaways$day, castaways$immunity_idols_won)

castaways$is_winner = ifelse(castaways$result == 'Sole Survivor', TRUE, FALSE)

plot(castaways$day, castaways$immunity_idols_won, col = ifelse(castaways$result == 'Sole Survivor', "green", "black"))

```
# Show Rating - 

Has the show popularity decline/quality? (sort by color)

```{r}
p <- viewers %>% 
  ggplot(aes(x=episode_date, y=viewers)) +
    geom_area(fill="#69b3a2", alpha=0.5) +
    geom_line(color="#69b3a2") +
    ylab("Viewers (millions") + 
    xlab("Date") +
    theme_ipsum() 

ggplotly(p)

```

### IMDB Rating

```{r}

```

# Jury

### How many votes did the final 3 get?

```{r}

jury_votes %>% 
  select(-c(castaway, castaway_id)) %>% 
  group_by(season, finalist) %>% 
  mutate(votes = sum(vote)) %>% 
  select(-c(vote)) %>% 
  unique() %>% 
  arrange(season, desc(votes))
  

```



### Voting History

```{r}
ranking <- vote_history %>% 
  distinct(season_name, order, voted_out)


ranking
```

## Crazy Voting Outcomes

```{r}
# Tie


# Idol nullfiers

```



